The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-06 methods/ms.tex
Testing ...
Progress, of a sort.

% Figure list
% 1) fig:Coverage
% 2) fig:BGPSMontage
% 3) fig:Bandpass
% 4) fig:Array
% 5) fig:CalibrationCurves
% 6) fig:Flatfield
% 7) fig:CygnusComparison
% 8) fig:PointingCalibrators

@@

\section{Flux Density and Surface Brightness Calibration}

@@

\Figure{relsens_cal}{An illustration of the relative sensitivity
calibration using the atmosphere as a calibrator.  Black is the median
over all bolometers (the atmosphere model), red and green are
individual bolometers. a. before and b. after applying the relative
calibration.  Note the improved agreement.}{fig:Flatfield}{1.0}

\Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
in the same aperture from the \citet{motte07} MAMBO map and the
Bolocam map of this paper.}{fig:CygnusComparison}{1.0}

@@

\section{Astrometry}

@@

{\em Show a cross-correlation map?}

\subsection{Comparison to SCUBA and SHARC-II Positions}

The same cross-correlation procedure was used to compare to SCUBA maps where
available.  The morphological correlation between SCUBA and BGPS sources is
excellent, so cross-correlation maps could be used to test our pointing model.

@@

{\em Miranda's data here}

\FigureTwo{plane_astrometry}{pointing_model_skydist}{Left: The
distribution of absolute reference sources (crosses) in the Galactic
Plane (Appendix \ref{app:PointingCalibrators}).  Also shown (crosses)
are the locations of bright, isolated, compact sources for comparison
with other surveys, as given in Appendix \ref{app:ReferenceSources}.
Right: The distribution of the pointing calibration sources across the
local sky in Hawaii.  Notice the good sampling of the entire region
used for the Survey.}{fig:PointingCalibrators}{1.0}

\begin{figure}
  \subfigure[The pointing model correction (left) and residuals
(right) for Epoch V, from which the master reference images were
derived for subsequent alignment. {\em To be replaced with newer
figure?}]
{\label{fig:PointingModel-a}\includegraphics[scale=1.0]{pointing_model}}\\

  \subfigure[The residuals of the pointing model.  Note the Gaussian
distribution.]{\label{fig:PointingModel-b}\includegraphics[scale=0.7]{pointing_model_residuals}}

\caption{Pointing model.}
\end{figure}

@@

%\Figure{eachpca}{The effect of the number of iterations on
%the reduction process.}{fig:Iter}{1.0}

@@

\Figure{flagger_plots}{An illustration of a ``glitch'' in a single
bolometer timestream (red) due to a cosmic ray strike.  Note the
acausal ringing due to the application of the downsampling filter.
The time series for a physically adjacent bolometer is shown in blue,
and a bolometer which does not pass over a source in green.  The PCA
model has already been subtracted from the
data.}{fig:CosmicRayGlitch}{1.0}

\Figure{crs}{The distribution of glitch amplitudes flagged and
removed from the data.  The expected contribution to the noise from
the unremoved glitches below the detection threshold is
\TBD.}{fig:GlitchDistribution}{1.0}

@@

\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of the
flagging process using the waterfall plot. Left: The glitch apparent at middle
right is the same one whose time series is shown in Figure
\ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the effect of the
glitch also propagates over the other bolometers, appearing as a horizontal
stripe. Right: The same data displayed with the time point including the glitch
flagged out and rescaled}  {fig:Flag1}{1.0}

%this figure failed to create automatically and wasn't really that useful
%anyway
% \Figure{flagger_glitchboxflagged}{A box is drawn around the bad data and it is
% removed from subsequent analysis.}{fig:Flag2}{1.0}

% \Figure{flagger_glitchgone}{A rescaled version of the data with the
% bad data removed.  The effect of the glitch on the other bolometers is
% now more apparent; this too is flagged out in subsequent
% analysis.}{fig:Flag3}{1.0}

@@

@@

Figure \ref{fig:PCA_filter}a shows the fraction of flux recovered in the map as a
function of source size for a range of different PCA components subtracted in
the cleaning.  These measurements were produced by inserting simulated gaussian
sources at a range of peak flux densities and sizes spread out through the map
and summing the flux in an ellipse on the final cleaned map.

@@

%\Figure{esf}{The effective spatial filter applied to the Bolocam
%maps due to atmospheric cleaning.}{fig:ESF}{1.0}

@@

\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The fractional
flux recovered as a function of source size for well-separated Gaussian sources with
the FWHM as indicated.
\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13
(orange),16 (red),21 (teal),26 (lime),31 (black) PCA components subtracted.
\emph{Right}: 7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
kernel for 13 PCA components subtracted
}{fig:PCA_filter}{1.0}

>>>>

% Figure list
% 1) fig:Coverage
% 2) fig:BGPSMontage
% 3) fig:Bandpass
% 4) fig:Array
% 5) fig:CalibrationCurves
% 6) fig:Flatfield
% 7) fig:CygnusComparison
% 8) fig:PointingCalibrators
% 9) fig:PointingModel
% 10) fig:SCUBAPointingComparison
% 11) fig:IterativeMapping
% 12) fig:Flagging
% 13) fig:GlitchDistribution
% 14) fig:PCA_Filter
% 15) fig:Deconvolution

@@

\section{Flux Density and Surface Brightness Calibration}
\label{sec:FluxCalibration}

@@

% 6
\Figure{relsens_cal}{An illustration of the relative sensitivity
calibration using the atmosphere as a calibrator.  Black is the median
over all bolometers (the atmosphere model), red and green are
individual bolometers. a. before and b. after applying the relative
calibration.  Note the improved agreement.}{fig:Flatfield}{1.0}

% 7
\Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
in the same aperture from the \citet{motte07} MAMBO map and the
Bolocam map of this paper.}{fig:CygnusComparison}{1.0}

@@

\section{Astrometry}
\label{sec:Astrometry}

@@

\subsection{Comparison to SCUBA Legacy Source Positions}
\label{sec:SCUBAPointingComparison}
%and SHARC-II Positions}

The same cross-correlation procedure was used to compare to the SCUBA
maps from the Legacy Catalog.  The morphological correlation between
SCUBA and BGPS sources is excellent, so cross-correlation maps could
be used to test our pointing model.

An example is shown in Figure \ref{fig:SCUBAPointingComparison}.

{\it Do the negative bowls of either survey bunge up the
cross-correlation?  If not, how do we deal with them?}

@@

%{\em Miranda's data here}

% 8
% -----------------------------------------------------------------------------
\FigureTwo{plane_astrometry}{pointing_model_skydist}{Left: The
distribution of absolute reference sources (crosses) in the Galactic
Plane (Appendix \ref{app:PointingCalibrators}).  Also shown (crosses)
are the locations of bright, isolated, compact sources for comparison
with other surveys, as given in Appendix \ref{app:ReferenceSources}.
Right: The distribution of the pointing calibration sources across the
local sky in Hawaii during the July 2007 epoch when the pointing model
was constructed.  Notice the good sampling of the entire region used
for the Survey.}{fig:PointingCalibrators}{1.0}
% -----------------------------------------------------------------------------

% 9
% -----------------------------------------------------------------------------
\begin{figure}
  \subfigure[The pointing model correction (left) and residuals
(right) for Epoch V, from which the master reference images were
derived for subsequent alignment. {\em To be replaced with newer
figure?}]
{\label{fig:PointingModel-a}\includegraphics[scale=1.0]{pointing_model}}\\

  \subfigure[The residuals of the pointing model.  Note the Gaussian
distribution.]
{\label{fig:PointingModel-b}\includegraphics[scale=0.5]{pointing_model_residuals}}

\caption{The Bolocam pointing model for Epoch V.}
\label{fig:PointingModel}
\end{figure}
% -----------------------------------------------------------------------------

% 10
% -----------------------------------------------------------------------------
\begin{figure}

  \subfigure[{\it Left}: the Bolocam map in a portion of the $l=30$
  field.  {\it Right}: the SLC maps in the same region.  The green
  contours on the Bolocam map indicate the positions of the SLC
  sources.]
  {\label{fig:SCUBAPointingComparison-a}\includegraphics[scale=0.8]
  {scuba_bolocam_l030}}

  \begin{tabular}{cc}

  \subfigure[The cross-correlation map of the BGPS and SLC maps in
  Figure \ref{fig:SCUBAPointingComparison-a}. {\bf to be replaced with
  correct map}]
  {\label{fig:SCUBAPointingComparison-b}\includegraphics[scale=0.45]
  {xcorr_standin}}

  \subfigure[The measured offset between Bolocam and SCUBA Legacy
sources \citep{difrancesco08}, using the method described in Setion
\ref{sec:SCUBAPointingComparison}.  The circle indicates the $1\sigma$
region, which is also consistent with the error derived from the
internal Bolocam pointing model.]
{\label{fig:SCUBAPointingComparison-c}\includegraphics[scale=0.45]
{scuba_pointing_offsets}}

\end{tabular}

\caption{Comparing the Bolocam positions to those of the SCUBA Legacy Catalog.}
\label{fig:SCUBAPointingComparison}
\end{figure}
% -----------------------------------------------------------------------------

@@

@@

@@

@@

\setcounter{subfig}{1}
\renewcommand{\thefigure}{\arabic{figure}\alph{subfig}}

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{iterative_mapping1}
      \caption{An example of the change in the time series as
      iterative mapping proceeds.}
    \end{center}
    \label{fig:IterativeMapping}
  \end{minipage}
\end{figure}

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{iterative_mapping2}
      \caption{}
    \end{center}
    \label{fig:IterativeMapping-b}
  \end{minipage}
\end{figure}

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{iterative_mapping3}
      \caption{}
    \end{center}
    \label{fig:IterativeMapping-c}
  \end{minipage}
\end{figure}

% -----------------------------------------------------------------------------
\setcounter{subfig}{1}
\begin{figure}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_withglitch}
    \end{center}
  \end{minipage}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_glitchgone}
    \end{center}
  \end{minipage}
  \caption{An illustration of the flagging process using the waterfall
plot. Left: The glitch apparent at middle right is the same one whose
time series is shown in Figure \ref{fig:CosmicRayGlitch}.  Because of
the PCA subtraction, the effect of the glitch also propagates over the
other bolometers, appearing as a horizontal stripe. Right: The same
data displayed with the time point including the glitch flagged out
and rescaled}

  \label{fig:Flagger}

  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_plots}
      \caption{An illustration of a ``glitch'' in a single bolometer
timestream (red) due to a cosmic ray strike.  Note the acausal ringing
due to the application of the downsampling filter.  The time series
for a physically adjacent bolometer is shown in blue, and a bolometer
which does not pass over a source in green.  The PCA model has already
been subtracted from the data.}
    \end{center}
  \end{minipage}

\end{figure}

% -----------------------------------------------------------------------------

%\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of
%the flagging process using the waterfall plot. Left: The glitch
%apparent at middle right is the same one whose time series is shown in
%Figure \ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the
%effect of the glitch also propagates over the other bolometers,
%appearing as a horizontal stripe. Right: The same data displayed with
%the time point including the glitch flagged out and rescaled}
%{fig:Flaggin}{1.0}
%
\Figure{crs}{The distribution of glitch amplitudes flagged and removed
from the data.  The expected contribution to the noise from the
unremoved glitches below the detection threshold is
\TBD.}{fig:GlitchDistribution}{1.0}

@@

Figure \ref{fig:PCA_Filter}a shows the fraction of flux recovered in the map as a
function of source size for a range of different PCA components subtracted in
the cleaning.  These measurements were produced by inserting simulated gaussian
sources at a range of peak flux densities and sizes spread out through the map
and summing the flux in an ellipse on the final cleaned map.

@@

@@

\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The
fractional flux recovered as a function of source size for
well-separated Gaussian sources with the FWHM as indicated.
\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13 (orange),16 (red),21
(teal),26 (lime),31 (black) PCA components subtracted.  \emph{Right}:
7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
kernel for 13 PCA components subtracted }{fig:PCA_Filter}{1.0}
